---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Press+Start+2P&family=Rubik+Doodle+Shadow&display=swap');

body {
    background-color: black;
    color: white;
    font-family: 'Press Start 2P', cursive;
    line-height: 1.6;
}

h1 {
    font-family: 'Rubik Doodle Shadow', sans-serif;
    color: red;
    letter-spacing: 2px;
}

h2 {
    color: green;
    font-size: 24px;
}
```

## Daily Gaming Analysis
I gathered daily gaming behaviors from about 20 people, extracting data points such as: How many hours do you spend gaming every day? What do you think the length of time you spend playing is related to? Which genre do you play the most? What platform do you game on? The study focused on quantifying and qualifying various aspects of their daily gaming routines through data.

```{r}
library(tidyverse)

# Read data directly from the URL
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRS0E1iAwBvjsIrzjcDumrSjZheHa6cCLiPrLW7R2erUSHlkttGjIys7tRCuU1NU5duGS4gkitjIllr/pub?gid=1571160482&single=true&output=csv")
logged_data

# Use the rename() function, create a new data frame named latest_data
latest_data <- logged_data %>% 
  rename(time = 1,
         time_hours = 2,
         time_related = 3,
         game_genre = 4,
         game_platform = 5)

names(latest_data)
glimpse(latest_data)

# Calculate how many answers in total:
total_answer_time_hours <- length(na.omit(latest_data$time_hours))
total_answer_time_hours

# Since we know the time_hours is numeric, I can use r function to explore the data
min_time_hours <- min(latest_data$time_hours, na.rm = TRUE)
max_time_hours <- max(latest_data$time_hours, na.rm = TRUE)
mean_time_hours <- mean(latest_data$time_hours, na.rm = TRUE)
min_time_hours
max_time_hours
mean_time_hours

# Create the bar char
# time_hours
ggplot(data = latest_data)  + 
  geom_bar(aes(x = time_hours),
           fill = "orange") +
  labs(title = "How many hours do you spend gaming every day?",
       x = "time_hours(per day)",
       y = "numbers")
# game_genre
ggplot(data = latest_data) + 
  geom_bar(aes(x = game_genre),
           fill = "red") +
  labs(title =  "Which genre do you play the most?",
       x = "game genre",
       y = "count of numbers")

# One commented section
paste0("The average daily gaming time of ", total_answer_time_hours, " participants is ", mean_time_hours, " hours")
paste0("There are ", total_answer_time_hours," people in total answer the question : How many hours do you spend gaming every day?")

```

